Compiling refinement types to dependent types

### 2020-07-24 tex/paper.tex
Some yak shaving for TODOs
Formulate some lemmas about the core language

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{hyperref,cleveref}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}
\usepackage{cite,url,babelbib}
\usepackage[english]{babel}

@@

@@

    %TODO the { v : B | T } in the Γ' desugars to a dependent pair, yet we use λv : \hat B — note the naked base type.
    %Figure out how to best fix this.

@@

    We resort to \textsc{CT-Form} on the right.
    This is well-formed,
    since $\Tranty(\nonterm G \vdash \nonterm{ts}_1)$ produces a derivation of $\nonterm{GC} \vdash \nonterm{tc}_1 : \star$,
    and similarly we get a derivation of $\nonterm{GC}, \gterm x : \nonterm{tc}_1 \vdash \nonterm{tc}_2 : \star$ from
    the other invocation of $\Tranty$.
\end{itemize}

>>>>

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{hyperref,cleveref}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}
\usepackage{cite,url,babelbib}
\usepackage{todonotes}
\usepackage[english]{babel}

@@

\subsubsection{Properties}

\begin{lemma}
  If $\nonterm G \vdash \nonterm{es} : \nonterm{ts}$, then $\nonterm G \ctxok$.
\end{lemma}
\begin{proof}
  \todo[inline]{Do the proof and remove the assumption $\nonterm G \ctxok$ from all the rules unless needed.}
\end{proof}

\begin{lemma}
  If $\nonterm G \vdash \nonterm{es} : \nonterm{ts}$, then $\nonterm G \vdash \nonterm{ts}$.
\end{lemma}
\begin{proof}
  \todo[inline]{Do the proof.}
\end{proof}

@@

    \todo[inline]{
      The ${ v : B | \top }$ in the $\nonterm G '$ desugars to a dependent pair, yet we use $\lambda v : \hat B$ — note the naked base type.
      Figure out how to best fix this.
    }

@@

    We resort to \textsc{CT-Form} on the right.
    This is well-formed,
    since $\Tranty(\nonterm G \vdash \nonterm{ts}_1)$ produces a derivation of $\nonterm{GC} \vdash \nonterm{tc}_1 : \star$,
    and similarly we get a derivation of $\nonterm{GC}, \gterm x : \nonterm{tc}_1 \vdash \nonterm{tc}_2 : \star$ from
    the other invocation of $\Tranty$.
  \item \textsc{TWF-Rec}.
    \todo[inline]{Don't forget to define this.}
\end{itemize}
